### 2020-06-01 paper.tex
Add References Section

\bibitem{b1} H.S. Behera, Reena Kumari Naik, Suchilagna Parida, ``Improved multilevel feedback queue scheduling using dynamic time quantum and its performance analysis'', \textit{International Journal of Computer Science and Information Technologies}, vol. 3, no. 2, 2012, pp. 3801-3807.

\bibitem{b2} MohammadReza EffatParvar, Karim Faez, Mehdi EffatParvar, Mehdi Zarei, Saeed Safari, ``An intelligent MLFQ scheduling algorithm (IMLFQ) with fault tolerant mechanism'', \textit{Sixth International Conference on Intelligent Systems Design and Applications}, vol. 3, 2006, pp. 80–85.

\bibitem{b3} Rakesh Mohanty, H. S. Behera, Khusbu Patwari, Monisha Dash, ``Design and performance evaluation of a new proposed shortest remaining burst round robin (SRBRR) scheduling algorithm'', \textit{International Symposium on Computer Engineering \& Technology}, vol. 17, 2010.

\bibitem{b4} S. K. Dwivedi and R. Gupta, ``A simulator based performance analysis of multilevel feedback queue scheduling'', \textit{2014 International Conference on Computer and Communication Technology (ICCCT)}, Allahabad, 2014, pp. 341-346.

\bibitem{b5} Malhar Thombare, Rajiv Sukhwani, Priyam Shah, Sheetal Chaudhari, Pooja Raundale, ``Efficient implementation of multilevel feedback queue scheduling'', \textit{2016 International Conference on Wireless Communications, Signal Processing and Networking (WiSPNET)}, Chennai, 2016, pp. 1950–1954.

\bibitem{b6} S. Raheja, R. Dadhich, and S. Rajpalc, ``Designing of vague logic based multilevel feedback queue scheduler'', \textit{Egyptian Informatics Journal}, vol. 17, 2016, pp. 125-137.

\bibitem{b7} A. Alsheikhy, R. Ammar and R. Elfouly, ``An improved dynamic Round Robin scheduling algorithm based on a variant quantum time'', \textit{2015 11th International Computer Engineering Conference (ICENCO)}, Cairo, 2015, pp. 98-104.

\bibitem{b8} M. K. Mishra and F. Rashid, ``An improved round robin CPU scheduling algorithm with varying time quantum'', \textit{International Journal of Computer Science, Engineering and Applications  (IJCSEA)}, vol. 4, 2014.

\bibitem{b9} A. Singh, P. Goyal and S. Batra, ``An optimized round robin scheduling algorithm for CPU scheduling'', \textit{International Journal on Computer Science and Engineering}, 2010, pp. 2383-2385.

\bibitem{b10} Dipto Biswas, Md. Samsuddoha, ``Determining proficient time quantum to  improve the performance  of  round  robin  scheduling  algorithm'', \textit{International  Journal  of  Modern  Education  and  Computer Science(IJMECS)}, vol. 11, 2019, pp. 33-40.

\bibitem{b11} K. Hoganson and J. Brown, ``Real-time scheduling with MLFQ-RT multilevel feedback queue with starvation mitigation'', \textit{2017 International Conference on Engineering, Technology and Innovation (ICE/ITMC)}, Funchal, 2017, pp. 155-160.

>>>>

\bibitem{b1} Saab, Youssef, ``A fast clustering-based min-cut placement algorithm with simulated-annealing performance'', \textit{VLSI Design}, vol. 5, no. 1, 1996, pp. 37-48.

\bibitem{b2} H. Esbensen, ``A genetic algorithm for macro cell placement'', \textit{European Design Automation Conference}, Hamburg, Germany, 1992, pp. 52-57.

\bibitem{b3} K. Shahookar and P. Mazumder, ``GASP-a genetic algorithm for standard cell placement'', \textit{Proceedings of the European Design Automation Conference}, Glasgow, UK, 1990, pp. 660-664.

\bibitem{b4} J. Vygen, ``Algorithms for detailed placement of standard cells'', \textit{Proceedings Design, Automation and Test in Europe}, Paris, France, 1998, pp. 321-324.

\bibitem{b5} Min Pan, N. Viswanathan and C. Chu, ``An efficient and effective detailed placement algorithm'', \textit{ICCAD-2005. IEEE/ACM International Conference on Computer-Aided Design, 2005}, San Jose, CA, USA, 2005, pp. 48-55.

\bibitem{b6} Z. Jiang, H. Chen, T. Chen and Y. Chang, ``Challenges and Solutions in Modern VLSI Placement'', \textit{2007 International Symposium on VLSI Design, Automation and Test (VLSI-DAT)}, Hsinchu, 2007, pp. 1-5.

\bibitem{b7} Elhaddad, Younis, ``Combined simulated annealing and genetic algorithm to solve optimization problems'', \textit{World Academy of Science, Engineering and Technology}, 2012.

\bibitem{b8} N. Viswanathan and C. C. -. Chu, ``FastPlace: efficient analytical placement using cell shifting, iterative local refinement,and a hybrid net model'', \textit{IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems}, vol. 24, no. 5, May 2005, pp. 722-733.

\bibitem{b9} D. Zaporozhets, D. Zaruba and N. Kulieva, ``Hybrid heuristic algorithm for VLSI placement'', \textit{2019 International Russian Automation Conference (RusAutoCon)}, Sochi, Russia, 2019, pp. 1-5.

\bibitem{b10} R. F. Hentschke and R. A. D. L. Reis, ``Improving simulated annealing placement by applying random and greedy mixed perturbations [IC layout]'', \textit{16th Symposium on Integrated Circuits and Systems Design, 2003. SBCCI 2003. Proceedings}, Sao Paulo, Brazil, 2003, pp. 267-272.

\bibitem{b11} K. Vorwerk, A. Kennings and J. W. Greene, ``Improving Simulated Annealing-Based FPGA Placement With Directed Moves'', \textit{IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems}, vol. 28, no. 2, Feb. 2009, pp. 179-192.

\bibitem{b12} Atanu Roy, Karthik Ganesan Pillai, ``Parallel simulated annealing for VLSI
cell placement problem'', 2009.

\bibitem{b13} J. A. Chandy and P. Banerjee, ``Parallel simulated annealing strategies for VLSI cell placement'', \textit{Proceedings of 9th International Conference on VLSI Design}, Bangalore, India, 1996, pp. 37-42.

\bibitem{b14} J. W. Greene and K. J. Supowit, ``Simulated annealing without rejected moves'', \textit{IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems}, vol. 5, no. 1, January 1986, pp. 221-228.

\bibitem{b15} A. B. Kahng and S. Reda, ``Wirelength minimization for min-cut placements via placement feedback'', \textit{IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems}, vol. 25, no. 7, July 2006, pp. 1301-1312.
